Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2025-01-24 manuscript/ms (2).tex
Update ms (2).tex
Update methods

We estimated \begin{math}\mu_t\end{math} and \begin{math}\theta_t\end{math} using iteratively reweighted least-squares (procedure implemented via the NBPSeq R package \cite{NBPSeq}) using a window around each time step.
For each window, a series of \begin{math}\mu_t\end{math} was estimated using a spline function in time, and a single value of \begin{math}\theta\end{math} was estimated for that window. 
By moving the window one time step at a time, a time series of \begin{math}\theta_t\end{math} was produced. We investigated large counties (the three counties with the largest populations in each state), due to power constraints and convergence issues.

>>>>

For each time step in each empirical epidemic curve, a series of \begin{math}\mu_t\end{math} and a single value of \begin{math}\theta\end{math} was estimated for the corresponding window. 
By moving the window one time step at a time, time series of \begin{math}\theta\end{math} estimates and p-values were produced. We investigated large counties (the three counties with the largest populations in each state).
